---
title: "Data Visualization Solutions"
author: "R for the Rest of Us"
output: 
    html_document:
        css: slides/style.css
        toc: true
        toc_depth: 1
        toc_float: true
        df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages

Let's load the `tidyverse` package. 

```{r}
library(tidyverse)
```

# Import NHANES Data

Import your data into a data frame called NHANES. 

```{r}
nhanes <- read_csv("data/nhanes.csv")
```


# Scatterplot

Make a scatterplot that shows weight on the x axis and height on the y axis.

```{r}
ggplot(data = nhanes,
       mapping = aes(x = weight,
                     y = height)) +
  geom_point()
```



# Histogram 

Make a histogram that shows the distribution of the weight variable.


```{r}
ggplot(data = nhanes,
       mapping = aes(x = height)) +
  geom_histogram()
```

Copy your code from above, but adjust it so that there are 50 bins.

```{r}
ggplot(data = nhanes,
       mapping = aes(x = height)) +
  geom_histogram(bins = 50)
```

# Bar Chart

## Bar Chart v1

Use the v1 approach to make a bar chart that shows a count of the number of people who say they smoke. Include NA responses.


```{r}
ggplot(data = nhanes,
       mapping = aes(x = smoke_now)) +
  geom_bar()
```



## Bar Chart v2

I've made a new data frame called `sleep_by_gender` that shows the average amount of sleep per night that males and females report getting. 

```{r}
sleep_by_gender <- nhanes %>% 
  group_by(gender) %>% 
  summarize(avg_sleep = mean(sleep_hrs_night, na.rm = TRUE)) 
```

Plot the average amount of sleep per night for males and females.

```{r}
ggplot(data = sleep_by_gender,
       mapping = aes(x = gender,
                     y = avg_sleep)) +
  geom_bar(stat = "identity")
```




# `color` and `fill`

Take your bar chart from above and make the inside of each bar a different color.

```{r}
ggplot(data = sleep_by_gender,
       mapping = aes(x = gender,
                     y = avg_sleep,
                     fill = gender)) +
  geom_bar(stat = "identity")
```

Make your scatterplot from before that shows weight on the x axis and height on the y axis again, but make the dots show up in different colors based on the `race1` variable.

```{r}
ggplot(data = nhanes,
       mapping = aes(x = weight,
                     y = height,
                     color = race1)) +
  geom_point()
```




# Plot Labels

Use the scatterplot from above and do the following:

1. Add a title
2. Add a better x and y axis label

```{r}
ggplot(data = nhanes,
       mapping = aes(x = weight,
                     y = height,
                     color = race1)) +
  geom_point() +
  labs(title = "Association Between Weight and Height by Race",
       x = "Weight",
       y = "Height")
```



# Themes

Use the code chunk from above and then add the `theme_minimal` to your plot.

```{r}
ggplot(data = nhanes,
       mapping = aes(x = weight,
                     y = height,
                     color = race1)) +
  geom_point() +
  labs(title = "Association Between Weight and Height by Race",
       x = "Weight",
       y = "Height") +
  theme_minimal()
```

# Facets

Use the code chunk from above and make a facetted scatterplot by the `race1` variable.

```{r}
ggplot(data = nhanes,
       mapping = aes(x = weight,
                     y = height,
                     color = race1)) +
  geom_point() +
  labs(title = "Association Between Weight and Height by Race",
       x = "Weight",
       y = "Height") +
  theme_minimal() +
  facet_wrap(~race1)
```
