---
title: "Data Visualization Exercises"
author: "R for the Rest of Us"
output: 
    html_document:
        css: slides/style.css
        toc: true
        toc_depth: 1
        toc_float: true
        df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages

Let's load the `tidyverse` package. 

```{r}
library(tidyverse)
```

# Import NHANES Data

Import your data into a data frame called NHANES. 

```{r}
nhanes <- read_csv("data/nhanes.csv")
```


# Scatterplot

Make a scatterplot that shows weight on the x axis and height on the y axis.

```{r}
# YOUR CODE HERE 
```



# Histogram 

Make a histogram that shows the distribution of the weight variable.


```{r}
# YOUR CODE HERE 
```

Copy your code from above, but adjust it so that there are 50 bins.

```{r}
# YOUR CODE HERE 
```

# Bar Chart

## Bar Chart v1

Use the v1 approach to make a bar chart that shows a count of the number of people who say they smoke. Include NA responses.


```{r}
# YOUR CODE HERE 
```



## Bar Chart v2

I've made a new data frame called `sleep_by_gender` that shows the average amount of sleep per night that males and females report getting. 

```{r}
sleep_by_gender <- nhanes %>% 
  group_by(gender) %>% 
  summarize(avg_sleep = mean(sleep_hrs_night, 
                             na.rm = TRUE)) 
```

Plot the average amount of sleep per night for males and females.

```{r}
# YOUR CODE HERE 
```




# `color` and `fill`

Take your bar chart from above and make the inside of each bar a different color.

```{r}
# YOUR CODE HERE 
```

Make your scatterplot from before that shows weight on the x axis and height on the y axis again, but make the dots show up in different colors based on the `race1` variable.

```{r}
# YOUR CODE HERE 
```


# Plot Labels

Use the scatterplot from above and do the following:

1. Add a title
2. Add a better x and y axis label

```{r}
# YOUR CODE HERE 
```



# Themes

Use the code chunk from above and then add the `theme_minimal` to your plot.

```{r}
# YOUR CODE HERE 
```

# Facets

Use the code chunk from above and make a facetted scatterplot by the `race1` variable.

```{r}
# YOUR CODE HERE 
```

